Supplement: Bootstrapping Domain Specific Languages for Bayesian Program Learning

### 2018-02-09 supplement.tex
(supplement) make string editing sentence less awkward
hyper parameters

>>>>

\vfill

\section{Hyperparameters \& Implementation details}
We set $\alpha = 10$ and $\lambda = 1$ for all experiments except for string
editing. For string editing we found that more strongly regularizing
the DSL was necessary,
and so we set $\lambda = 5$.
We believe this is because
we have many more tasks for string editing than we do for the other domains.
The frontier size used for Boolean circuits was $5000$,
for symbolic regression we used $500$,
for string editing we used $10^5$,
and for list functions we used $10^4$.

Because the frontiers can become very large in later iterations of the algorithm,
we only keep around the top $10^4$ programs in the frontier $\mathcal{F}_x$ as measured by $\probability[x,p|\mathcal{D},\theta]$.
